Dynamic Knapsack Problem

### 2021-05-16 Manuscript/Manuscript.tex
things todo
todo:
- move uv to action
- change cost to be post-action states
- add auxiliary post-action states
- add carry over in the simulation
Finalized Model Update and Myopic and MDP Simulation
to finish - FAS simulation

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}

\usepackage{hyperref}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

\geometry{margin=1in}
\setlength\parindent{0pt}

\title{Dynamic Knapsack Problem}
\author{KV}
\date{February 2021}

\begin{document}

\maketitle
\tableofcontents

@@

\subsection{Questions}
\begin{itemize}
	\item Need to change generating an action section (4.7)
	\item Priority need to be added
	\item PPE resources need to include OR time
	\item When generating a new state for master (section 4.5), do I need to ensure the states are consistent, etc?
\end{itemize}

@@

	\item It is assumed that there is a certain default expected number of PPE units available for all periods
		\begin{itemize}
			\item However, in the period 1, there is some random deviation from the expected number of units
			\item This random deviation follows some uniform distribution
		\end{itemize}
\end{itemize}

\section{MDP Model}
\subsection{Decision Epochs}
Decisions are made at the beginning of each time period (will be weeks)

\subsection{State Space}
\subsubsection{Description}
State space is defined by current units available for various PPEs for future periods, amount of units already used for various PPEs, current patient waitlist, expected period demand, and number of patients already scheduled
\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{uv}, \vec{pw}, \vec{ps}) \]
\begin{itemize}
    \item $\vec{ue} = ue_{tp}$ - Expected unist for period $t$, and PPE $p$
    \item $\vec{uu} = uu_{tp}$ - Used units for period $t$, and PPE $p$
    \item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of PPE $p$
    \item $\vec{pw} = pw_{mdc}$ - Number of patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0, stands for people who just arrived)
    \item $\vec{ps} = ps_{tmdc}$ - Number of patients of complexity $d$, CPU $c$, scheduled to period $t$, who have been on the waitlist for $m$ periods ($m$ of 0 stands for people who have just arrived)
\end{itemize}
\subsubsection{States Constraints}
\begin{itemize}
	\item PPE Usage Constraint
	\begin{equation}
		uu_{tp} = ue_{tp}+uv_{tp} \quad \forall tp
	\end{equation}
	\item Bounds on states
	\begin{itemize}
		\item $ue_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
		\item $uu_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
		\item $uv_{tp} \le uen_{p} + max(ued_p) \quad \forall tp$
		\item $pw_{mdc} \le pea_{dc} * 4 \quad \forall mdc$
		\item $ps_{tmdc} \le pea_{dc} * 4 \quad \forall tmdc$
	\end{itemize}
\end{itemize}

\subsection{Action Sets}
\subsubsection{Description}
At the beginning of each period, decision maker must reschedule appointments as necessary (if patient complexity increased and too much PPE is being used, or if expected units of PPE have changed negatively). And decision maker must also schedule patients to surgeries
\[  \vec{A} = (\vec{sc}, \vec{rsc}) \] 
\begin{itemize}
    \item $\vec{sc} = sc_{tmdc}$ - Number of patients of difficulty $d$, CPU $c$, who have been in wait list for $m$ periods, to schedule in period $t$ ($m$ of 0 stands for people who have just arrived)
	\item $\vec{rsc} = rsc_{tt'mdc}$ - Number of patients of difficulty $d$, CPU $c$, who have been on the waitlist for $m$ periods, to reschedule from period $t$ to period $t'$
\end{itemize}

\subsubsection{Action Constraints}
\label{action constraints}
\begin{itemize}
    \item Tracks PPE Usage  
    \begin{itemize}
    		\item ($U_{pdc}$ - usage of PPE $p$ per patient difficulty $d$, CPU $c$)
    \end{itemize}
        \begin{equation} 
			(\sum_{mdc}ps_{tmdc} + \sum_{mdc}sc_{tmdc} + 
			\sum_{tmdc} rsc_{tt'mdc} - \sum_{t'mdc} rsc_{tt'mdc})U_{pdc} = uu_{tp}\ \quad \forall tp
		\end{equation}

	\item Bounds on when reschedules are allowed
		\begin{equation}  
			rsc_{tt'mdc} = 0 \quad \forall t \in \{ 2...T \}, t' \in \{2...T\} mdc 
		\end{equation} 
		\begin{equation}  
			rsc_{tt'mdc} = 0 \quad \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc 
		\end{equation} 
		\begin{equation}  
			rsc_{tt'mdc} = 0 \quad \forall tt'mdc, \text{where } t=t' 
		\end{equation}

	\item Cap on max schedule/reschedule wait time
		\begin{equation}  
			\sum_{tmdc} sc_{tmdc} = 0 \quad \text{where } t+m-1 > 2Tl 
		\end{equation} 
		\begin{equation}  
			\sum_{tt'mdc} rsc_{tt'mdc} \quad \text{where } t'+m+1 > 2Tl 
		\end{equation}

	\item number of people scheduled/rescheduled must be consistent
		\begin{equation}  
			\sum_{t'} rsc_{tt'mdc} \le ps_{tmdc} \quad \forall tmdc 
		\end{equation} 
		\begin{equation}  
			\sum_{t} sc_{tmdc} \le pw_{mdc} \quad \forall mdc 
		\end{equation} 
\end{itemize}

@@

	\item Number of patients arriving this period - $pe_{dc}$
		\begin{itemize}
			\item let's assume $pea_{dc}$ - is the random variable that represents the number of patients arrived this period. It follows a poisson distribution.
		\end{itemize}

	\item Transition between patient difficulties within the wait list - $pw_{mdc}$
		\begin{itemize}
			\item let's assume $pwt_{mdc}$ is the random variable that represents the number of patients of priority $d$, CPU $c$, that have been waiting for $m$ period, that have moved a more complex category. It follows binary distribution.
		\end{itemize}

	\item Transition between patient difficulties within the scheduled list - $ps_{tmdc}$
		\begin{itemize}
			\item let's assume $pst_{tmdc}$ is the random variable that represents the number of patients of priority $d$, CPU $c$, that have been waiting for $m$ period, that have been scheduled into period $t$, that have moved a more complex category. It follows binary distribution.
		\end{itemize}

	\item Amout of expected units of PPE resource for the next time period - $ue_{1p}$
		\begin{itemize}
			\item let's assume $ued_{p}$ is the random variable that represents the deviation of PPE units $p$ from the expectation for the next period only. It follows some uniform distribution.
			\item let's assume $uen_{p}$ is the default value to be used for expected number of PPE units $p$ per period
		\end{itemize}
\end{enumerate}

@@

\begin{enumerate}

	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Expected Units of PPE
		\begin{align} \begin{split}  
			ue'_{1p} = & ue_{2p} + ued_{p} + ue_{1p} - uu_{1p} - \\
				& - \sum_{mdc} sc_{1mdc}U_{pdc} + \sum_{t'mdc} rsc_{1t'mdc}U_{pdc} - \sum_{tmdc} rsc_{t1mdc}U_{pdc} \quad \forall p 
		\end{split} \end{align} 
		\begin{equation}  
			ue'_{t-1,p} = ue_{tp} \quad \forall t \in \{3...T\}, p
		 \end{equation} 
		\begin{equation}  
			ue'_{Tp} = uen_{p} \quad \forall p 
		\end{equation}

	\item Transition from $\vec{uu}$ to $\vec{uu'}$ - Used Units of PPE		
		\begin{align} \begin{split}  
			uu'_{t-1,p} = &  uu	_{tp} + \sum_{mdc} ( sc_{tmdc} U_{pdc} ) - \\ 
								&	- \sum_{t'mdc} (rsc_{tt'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'mdc} U_{pdc}) + \\ 
								& 	+ \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc})  \quad \forall t \in \{2...T\}, p  
		\end{split} \end{align}
		\begin{equation}  
			uu'_{Tp} = 0 \quad \forall p 
		\end{equation}

	\item Transition from $\vec{uv}$ to $\vec{uv'}$ - Violation of PPE units
	\begin{equation}
		uv'_{tp} \ge uu'_{tp} - ue'_{tp} \quad \forall tp
	\end{equation}
	\begin{equation}
		uv'_{tp} \ge 0 \quad \forall tp
	\end{equation}
	\begin{equation}
		uv'_{tp} = \max \{0, uu'_{tp} - ue'_{tp} \} \quad \forall tp
	\end{equation}

	\item Transition from $\vec{pw}$ to $\vec{pw'}$ - Flow of patients between difficulties/scheduling/cancelling for waitlist
		\begin{equation}  
			pw'_{0dc} = pea_{dc} \quad \forall dc 
		\end{equation} 
		\begin{equation}  
			pw'_{m+1, dc} = pw_{mdc} - \sum_{t} sc_{tmdc} + pwt_{m,d-1,c} - pwt_{mdc} \quad \forall m \in \{0...M-2 \}, dc 
		\end{equation} 
		\begin{equation}  
			pw'_{Mdc} = \sum_{M-1}^M pw_{mdc} - \sum_{t,M-1}^{M} sc_{tmdc} + \sum_{M-1}^{M} pwt_{m,d-1,c} - 
			\sum_{M-1}^{M} pwt_{mdc}\quad \forall dc 
		\end{equation}

	\item Transition from $\vec{ps}$ to $\vec{ps'}$ - Flow of patiensts between difficulties/scheduling/cancelling for scheduled appointments
		\begin{equation}
			ps'_{t0dc} = 0 \quad \forall tdc
		\end{equation}
		\begin{align}  \begin{split}
			ps'_{t-1,m+1,dc} = & ps_{tmdc} +  \sum_{t} sc_{tmdc} - \sum_{t'} rsc_{tt'mdc} + \sum_{t} rsc_{tt'mdc} +\\ 
										& + pst_{tm,d-1,c} - pst_{tmdc} \quad \forall t \in \{2 ... T\},  m \in \{0... M-2 \}, dc 
		\end{split} \end{align} 
		\begin{align} \begin{split}  
			ps'_{t-1,Mdc} = & \sum_{M-1}^M ps_{mdc}  - \sum_{t,M-1}^{M} sc_{tmdc}  - \sum_{t'M-1}^M rsc_{tt'mdc} + \\
									& \sum_{t,M-1}^M rsc_{tt'mdc} + \sum_{M-1}^{M} pst_{tm,d-1,c} - \sum_{M-1}^{M} pst_{tm,d,c}
									\quad \forall t \in \{2...T \}, dc 
		\end{split} \end{align}		
		\begin{equation}  
			ps'_{Tmdc} = 0 \quad \forall mdc 
		\end{equation} 
\end{enumerate}

\subsection{Costs}
Cost will come from two source:  
\begin{itemize} 
	\item cost of waiting ($cw$) (comes from 2 things)
	\item cost of canceling ($cc$)
	\item goal variable (to eliminate constraint violation, but still allow it if necessary)
\end{itemize}

\begin{align} \begin{split}  
	\vec{C} = c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) = 
		& \sum_{mdc} cw_{m} (pw_{mdc} - \sum_{t} sc_{tmdc}) +  \\
		& \sum_{tdc} cw_{M} (ps_{tMdc}) (\text{ to prevent infinite rescheduling })+ \\
		& + cc \sum_{tt`mdc, \text{where } t' > t} rsc_{tt'mdc} - cc \sum_{tt`mdc, \text{where } t' < t} rsc_{tt'mdc} + \\ 
		& + M (uv_{tp})
\end{split} \end{align} 
$cw_{m}$ is computed as follows ($val$ is arbitrary number that describes cost growth):
	\begin{equation}  cw_{m} = val^m \quad \forall m \end{equation} 
$cc$ is some arbitrary value

@@

\subsection{Full LP} 
Given a full MDP model, the equivalent LP would look as follows 
(Note: there is a lot left out. $\vec{C}$ is defined above, all states, actions, and next states are all defined above). Probability distribution is not explicitly defined, but I am not sure if it is necessary
\begin{equation}
	\max_{\vec{v}} \sum \alpha (\vec{S}) v(\vec{S}) 
\end{equation}

subject to
\begin{equation}
	c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) v( \vec{S'} | \vec{S}, \vec{A}, \vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) \ge v(\vec{S}) \quad \forall \vec{S} \vec{A}
\end{equation}

\subsection{Full ADP LP }
Let's convert it into ADP. We do that by changing $v(\vec{S})$ to an approximation as follows:
\begin{align} \begin{split}
	v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) =  & \beta^0 +
		\sum_{tp} \beta_{tp}^{ue} ue_{tp} +
		\sum_{tp} \beta_{tp}^{uu} uu_{tp} + 
		\sum_{tp} \beta_{tp}^{uv} uv_{tp} + \\
		& + \sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
		\sum_{tmdc} \beta_{tmdc}^{ps} ps_{tmdc}
\end{split} \end{align}

This gives the following LP
\begin{equation}
	\max_{\vec{\beta}} \sum \alpha (\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps})
\end{equation}
Subject to:
\begin{align*}
	& c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued})  *  \\
		& \Bigg( \beta^{0} + \\ 
		& \bigg( \sum_{p} \beta_{1p}^{ue} 
			(ue_{2p} + ued_{p} + ue_{1p} - uu_{1p} - \sum_{mdc} sc_{1mdc}U_{pdc} + \sum_{t'mdc} rsc_{1t'mdc}U_{pdc} - \sum_{tmdc} rsc_{t1mdc}U_{pdc}) \bigg)  \\ 
		& \bigg( \sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} + 
				\sum_{p} \beta_{Tp}^{ue} uen_{d} \bigg) + \\
		& \bigg( \sum_{p} \beta_{Tp}^{uu} * 0 \bigg) + \\
		& \bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
				\Big( uu_{t+1,p} + \sum_{mdc} (sc_{t+1,mdc}U_{pdc})  - 
				\sum_{t'mdc} (rsc_{t+1,t'mdc} U_{pdc}) + \sum_{tmdc} (rsc_{tt'+1,mdc} U_{pdc})  + \\ 
				& \quad \quad \quad \quad \quad \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc}) \Big) \bigg) +  \\
		& \bigg( \sum_{tp} uv'_{tp} \bigg) + \\ 
			& \bigg( \sum_{dc} \beta_{0dc}^{pw} (pea_{dc}) \bigg) + \\
		&  \bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
			(pw_{m-1,dc} - \sum_{t} sc_{t,m-1,dc} + pwt_{m-1,d-1,c} - pwt_{m-1,dc}) \bigg) + \\
		& \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
			(\sum_{M-1}^{M} pw_{mdc} - \sum_{M-1,t}^{M} sc_{tmdc} + 
			\sum_{M-1}^{M} pwt_{m,d-1,c} - \sum_{M-1}^{M} pwt_{mdc}) \bigg) + \\
		& \bigg( \sum_{mdc} \beta_{Tmdc}^{ps} * 0  \bigg) + \\
		& \bigg( \sum_{t=1,m=1,dc}^{T-1,M-1} \beta_{tmdc}^{ps} 
			\Big( ps_{t+1m-1dc} - \sum_{t} sc_{t+1,m-1,dc} + 
			pst_{t+1,m-1,d-1,c} - pst_{t+1,m-1,dc} - \\
		& \quad \quad \quad \quad \quad \quad  \quad \quad- \sum_{t'} rsc_{t+1,t'm-1,dc} +  \sum_{t} rsc_{t,t'+1,m-1,dc} \Big) \bigg) + \\
		& \bigg( \sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
			\Big( \sum_{M-1}^{M} ps_{t+1,mdc} - \sum_{M-1,t}^{M} sc_{t+1,mdc} + 
			\sum_{M-1}^{M} pst_{t+1,m,d-1,c} - \sum_{M-1}^{M} pst_{t+1,mdc} - \\ 
			& \quad \quad \quad \quad \quad \quad \quad - \sum_{M-1,t'}^{M} rsc_{t+1,t'mdc} +  \sum_{M-1,t}^{M} rsc_{t,t'+1,mdc} \Big) \bigg) \\
		& \Bigg) \ge v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) \quad \forall \vec{S} \vec{A}
\end{align*}
\begin{equation*}
	\vec{\beta} \ge 0 \quad \forall \beta
\end{equation*}

>>>>

%%%~~~~~~~~~~~~~~~~~ Preamble ~~~~~~~~~~~~~~~~~~~~~~
\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}

\usepackage{xcolor, hyperref}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

\usepackage{geometry}
\geometry{margin=0.65in}
\setlength\parindent{0pt}

\title{Dynamic Knapsack Problem}
\author{AS, WM, KV}
\date{\today}

\allowdisplaybreaks

%%%~~~~~~~~~~~~~~~~~ Document ~~~~~~~~~~~~~~~~~~~~~~
\begin{document}

\maketitle
\tableofcontents
\newpage

@@

\subsection{Questions}
\begin{itemize}
	\item Priority need to be added
\end{itemize}

@@

	\item It is assumed that there is a certain default expected number of PPE units available for all periods
	\begin{itemize}
		\item However, in the period 1, there is some random deviation from the expected number of units
		\item This random deviation follows some uniform distribution
	\end{itemize}
	\item We allow some violation of PPE units, in rare cases (with high cost), in order to accomodate changes due to variability.
	\begin{itemize}
		\item If we have violation of PPE units - it reduces capacity in the future (Meaning violations are borrowed from future capacity)
	\end{itemize}
\end{itemize}

\section{MDP Model}
\subsection{Decision Epochs}
Decisions are made at the beginning of each time period. There are 3 relevant time intervals to look at:
\begin{itemize}
	\item Pre-decision state ($S$)
	\begin{itemize}
		\item Pre-decision state defines the initial state on which a decision is required
		\item This information drives decision making
	\end{itemize}

	\item Post-decision state ($\hat{S}$)
	\begin{itemize}
		\item Post-decision state is the time when the decision has been executed, but no new info came in
		\item This state defines the immediate cost of an action
	\end{itemize}

	\item Post-transition state ($S'$)
	\begin{itemize}
		\item This is the state when new information has come in (transition randomness). Defines next pre decision state
		\item It is primarily used to generate expectation for the ADP
	\end{itemize}
\end{itemize}

\subsection{State Space}
\subsubsection{Description}
State is defined by current available and used resources, patient waitlist/demand, and patients already scheduled
\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{pw}, \vec{ps}) \]
\begin{itemize}
    \item $\vec{ue} = ue_{tp}$ - Expected unist for  period $t$, and resource $p$
    \item $\vec{uu} = uu_{tp}$ - Used units for period $t$, and resource $p$
    \item $\vec{pw} = pw_{mdc}$ - Patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
    \item $\vec{ps} = ps_{tmdc}$ - Patients of complexity $d$, CPU $c$, scheduled to period $t$, waiting for $m$ periods ($m$ of 0 - just arrived)
\end{itemize}

\subsection{Action Sets}
\subsubsection{Description}
Decision consists of rescheduling currently scheduled patients, and scheduling patients on waitlist. There are also some goal and auxiliary variables
\[  \vec{A} = (\vec{sc}, \vec{rsc}, \vec{uv}, \text{auxiliary variables}) \] 
\begin{itemize}
    \item $\vec{sc} = sc_{tmdc}$ - Patients of complexity $d$, CPU $c$, waiting for $m$ periods, to schedule in period $t$
	\item $\vec{rsc} = rsc_{tt'mdc}$ -Patients of complexity $d$, CPU $c$, waiting for $m$ periods, to reschedule from period $t$ to period $t'$
	\item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of resource $p$
\end{itemize}

\subsubsection{Auxiliary Variables}
\begin{itemize}
	\item $\hat{uu}_{tp}$ - post-decision units used
	\item $\hat{pw}_{mdc}$ - post-decision patients waiting
	\item $\hat{ps}_{tmdc}$ - post-decision patients scheduled
\end{itemize}
\subsubsection{Auxiliary Variable Definition}
\label{auxiliary constraints}
\begin{alignat}{10}
	& \hat{uu}_{tp} 
		&& =  \sum_{mdc} U_{pdc} \hat{ps}_{tmdc} \quad
		&& \forall tp \\ 
	& \hat{pw}_{mdc} 
		&& = pw_{mdc} - \sum_{t} sc_{tmdc} \quad 
		&& \forall mdc \\ 
	& \hat{ps}_{tmdc} 
		&& = ps_{tmdc} + sc_{tmdc} + 
			\sum_{t} rsc_{tt'mdc} - \sum_{t'} rsc_{tt'mdc} \quad 
		&& \forall tmdc
\end{alignat}

\subsubsection{State-Action Constraints}
\label{state-action constraints}
\begin{itemize}

	\item Consistency Constraint
	\begin{equation}
		uu_{tp} = \sum_{mdc} U_{pdc} ps_{tmdc} \quad \forall tp
	\end{equation}
	\item Resource Usage Constraint
	\begin{equation}
		\hat{uu}_{tp} \le ue_{tp}+uv_{tp} \quad \forall tp
	\end{equation}

	\item Custom bounds on when reschedules are allowed
	\begin{alignat}{10}
		& rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 2...T \}, t' \in \{2...T\} mdc \\
		& rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc  \\
		& rsc_{tt'mdc} && = 0 \quad && \forall tt'mdc, \text{where } t=t' 
	\end{alignat}

	\item Bounds on Schedules/Reschedules
	\begin{alignat}{10}
		& \sum_{t'} rsc_{tt'mdc} 	&& \le ps_{tmdc} \quad  && \forall tmdc  \\
		& \sum_{t} sc_{tmdc} 		&& \le pw_{mdc} \quad 	&& \forall mdc 
	\end{alignat}

	\item Bounds on states
	\begin{alignat}{10}
		& ue_{tp} 	&& \le uen_{p} + max(ued_p) \quad 	&& \forall tp \\
		& uu_{tp} 	&& \le uen_{p} + max(ued_p) \quad 	&& \forall tp \\
		& pw_{mdc} 	&& \le pea_{dc} * 4 \quad 			&& \forall mdc \\
		& ps_{tmdc} && \le pea_{dc} * 4 \quad 			&& \forall tmdc
	\end{alignat}
\end{itemize}

@@

	\item Number of patients arriving this period - $pw_{0dc}$
		\begin{itemize}
			\item $pea_{dc}$ - represents the random number of patients arriving. Follows a poisson distribution.
		\end{itemize}

	\item Transition between patient complexities within the wait list - $pw_{m>=1,dc}$
		\begin{itemize}
			\item $pwt_{mdc}$ represents the random number of patients of complexity $d$, CPU $c$, waiting for $m$ period, who became more complex. Follows binomial distribution.
			\item $ptp_{mdc}$ represents transition probability to a higher complexity
		\end{itemize}

	\item Transition between patient complexities within the scheduled list - $ps_{tmdc}$
		\begin{itemize}
			\item $pst_{tmdc}$ represents the random number of patients of complexity $d$, CPU $c$, waiting for $m$ period, scheduled into $t$ period, who became more complex. Follows binomial distribution.
		\end{itemize}

	\item Amout of expected units of PPE resource for the next time period - $ue_{1p}$
		\begin{itemize}
			\item $ued_{p}$ represents the random deviation of resource $p$ from the expectation. Follows uniform distribution.
			\item $uen_{p}$ expected units of resource $p$ per period
		\end{itemize}
\end{enumerate}

@@

\begin{enumerate}
	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Expected Resources
	\begin{alignat}{10}
		& ue'_{1p} 
			&& 	= \overbrace{ ue_{2p} + ued_{p} }^\text{deviation}
				+ \overbrace{ ue_{1p} - \hat{uu}_{1p} }^\text{unused} \quad
			&& \forall p \in \{ \text{Carry Over Resources} \} \\
		& ue'_{1p} 
			&& 	= ue_{2p} + ued_{p} \quad
			&& \forall p \in \{ \text{Non Carry Over Resources} \} \\
		& ue'_{tp} 
			&& = ue_{t+1,p} \quad 
			&& \forall t \in \{2...T-1\} p \\
		& ue'_{Tp} 
			&& = uen_{p} \quad
			&& \forall p
	\end{alignat}

	\item Transition from $\vec{uu}$ to $\vec{uu'}$ - Used Resources	
	\begin{alignat}{10}
		& uu'_{tp}
			&& = \hat{uu}_{t+1,p} + 
				\overbrace{ \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc}) }^\text{
					change in complexities} \quad
			&& \forall t \in \{1...T-1\} \\
		& uu'_{Tp}
			&& = 0 \quad
			&& \forall p
	\end{alignat}

	\item Transition from $\vec{pw}$ to $\vec{pw'}$ - Flow of patients on waitlist
		\begin{alignat}{10}
			& pw'_{0dc} 
				&& = pea_{dc} \quad
				&& \forall dc \\  
			& pw'_{mdc} 
				&& = \hat{pw}_{m-1,dc} + 
				\overbrace{pwt_{m-1,d-1,c} - pwt_{m-1,dc}}^\text{
					change in complexities} \quad
				&& \forall m \in \{ 1...M-1 \} dc \\  
			& pw'_{Mdc} 
				&& = \sum_{M-1}^{M} \big( 
					\hat{pw}_{mdc} + 
					\overbrace{pwt_{md-1,c} - pwt_{mdc}}^\text{
						change in complexities} \big) \quad
				&& \forall dc
		\end{alignat}

	\item Transition from $\vec{ps}$ to $\vec{ps'}$ - Flow of patiensts scheduled
		\begin{alignat}{10}
			& ps'_{t0dc} 
				&& = 0 \quad
				&& \forall tdc \\  
			& ps'_{Tmdc} 
				&& = 0 \quad
				&& \forall mdc \\  
			& ps'_{tmdc} 
				&& = \hat{ps}_{t+1,m-1,dc} + 
				\overbrace{pst_{t+1,m-1,d-1,c} - pst_{t+1,m-1,dc}}^\text{
					change in complexities} \quad
				&& \forall t \in \{1...T-1\} m \in \{ 1...M-1 \} dc \\  
			& ps'_{tMdc} 
				&& = \sum_{M-1}^{M} \big( 
				\hat{ps}_{t+1mdc} + 
				\overbrace{pst_{t+1,md-1,c} - pst_{t+1,mdc}}^\text{
					change in complexities} \big) \quad
				&& \forall t \in \{1...T-1\} dc
		\end{alignat}
\end{enumerate}

\subsection{Costs}
Cost will come from 3 sources:  
\begin{itemize} 
	\item waiting ($cw$)
	\item rescheduling ($cc = \lceil cw^M \rceil$)
	\item resource violation ($M$)
\end{itemize}

\begin{equation}\begin{alignedat}{10}
	& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
		&& 
			\overbrace{ \sum_{mdc} cw^{m} (\hat{pw}_{mdc}) }^\text{
				cost of waiting}  + 
			\overbrace{ \sum_{tdc} cw^{M} (\hat{ps}_{tMdc})}^\text{
				prevent infinite reschedules} + \\
	&	&&  +
			\overbrace{
				cc \sum_{
				\substack{tt`mdc \\ t' > t}} 
				rsc_{tt'mdc}}^\text{Bad Reschedule} - 
			\overbrace{ 
				cc \sum_{
				\substack{tt`mdc \\ t' < t}}
				rsc_{tt'mdc}}^\text{Good Reschedule} + 
			M \sum_{tp} uv_{tp}
\end{alignedat}\end{equation}

@@

\subsection{Full LP} 
Given a full MDP model, the equivalent LP would look as follows:
\begin{equation}
	\max_{\vec{v}} \sum \alpha (\vec{S}) v(\vec{S}) 
\end{equation}

subject to
\begin{equation}
	c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p(\vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) v( \vec{S'} | \vec{S}, \vec{A}, \vec{pea}, \vec{pwt}, \vec{pst}, \vec{ued}) \ge v(\vec{S}) \quad \forall \vec{S} \vec{A}
\end{equation}

\section{Aproximate Dynamic Programming Model}
\subsection{Full ADP Model}
Let's convert it into ADP. We do that by changing $v(\vec{S})$ to an approximation as follows:
\begin{equation}\begin{alignedat}{10}
	& v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{ps}) 
		&& =  \beta^0 + \sum_{tp} \beta_{tp}^{ue} ue_{tp} +
			\sum_{tp} \beta_{tp}^{uu} uu_{tp} + \\
		& && + \sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
			\sum_{tmdc} \beta_{tmdc}^{ps} ps_{tmdc}
\end{alignedat} \end{equation}

This gives the following LP
\begin{equation}
	\max_{\vec{\beta}} \sum \alpha (\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps})
\end{equation}
Subject to:
\begin{equation}\begin{alignedat}{10}
\label{full-adp-equation}
	& c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p \Bigg( 
		\beta^0 + \\
	& 	\bigg( \sum_{p} \beta_{1p}^{ue} 
			(ue_{2p} + ued_{p} + ue_{1p} - \hat{uu}_{1p}) \bigg)+
		\bigg( \sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} \bigg)+ 
		\bigg( \sum_{p} \beta_{Tp}^{ue} uen_{d} \bigg) + \\
	& 	\bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
			( \hat{uu}_{t+1,p} + \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc})) \bigg) +
		\bigg( \sum_{p} \beta_{Tp}^{uu} * 0 \bigg) + \\
	& 	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
		\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
			(\hat{pw}_{m-1dc} + pwt_{m-1d-1c} - pwt_{m-1dc}) \bigg) + \\
	&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
			(\sum_{M-1}^{M} \hat{pw}_{mdc} + pwt_{md-1c} - pwt_{mdc})\bigg) + \\
	& 	\bigg( \sum_{tdc} \beta_{t0dc}^{ps} 0 \bigg) +
		\bigg( \sum_{mdc} \beta_{Tmdc}^{ps} 0 \bigg) +
		\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
			(\hat{ps}_{t+1m-1dc} + pst_{t+1m-1d-1c} - pst_{t+1m-1dc}) \bigg) + \\	
	&	\bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
			(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + pst_{t+1md-1c} - pst_{t+1mdc})) \bigg)
	\Bigg) \ge v(\vec{ue}, \vec{pw}, \vec{ps}) \quad \forall \vec{S} \vec{A}
\end{alignedat} \end{equation}
\begin{equation}
	\vec{\beta} \ge 0 \quad \forall \beta
\end{equation}
And all auxiliary constraints in "\nameref{auxiliary constraints}"

\subsection{Expectation ADP Model}
Steps for rearranging and converting the constraint (\ref{full-adp-equation}) into expectation:
\begin{itemize}
	\item $E[ued_p] = 0$
	\item $E[pwt_{mdc}] = ptp_{mdc} * \hat{pw}_{mdc}$ 
	\item $E[pst_{tmdc}] = ptp_{mdc} * \hat{ps}_{tmdc}$ 
\end{itemize}
